The impact of gas bulk rotation on the Lyman $\alpha$ line

### 2014-08-11 paper/referee-reply.tex

\section*{Details}

\subsection*{Sect. 3.1}

{\bf You say that “If the viewing angle is aligned with the rotation
  axis, $|\mu| \approx 1$, the Ly$\alpha$ line keeps in most of the
  cases a double peak”, isn’t it in all cases ?}

  Yes it is doubles peaked in all the studies cases. This is reflected
  in the text.

@@

\subsection*{Sect. 3.5}
{\bf The parameter a is not defined when you discuss Neufeld.}

The definition is now included in the last paragraph of the
introduction.

@@

\subsection*{Fig9}

{\bf Is Fig 9, left panel, for a central source ? Can you show the
  homogeneous case also ? You discuss in the referee repport that the
  distribution is not bimodal anymore. But it has to be different than
  in central case, spanning the whole range of nb scatt, because
  photons are emitted at every radii in the cloud, so at every optical
  depth. On the right panel, solid and dashed lines are not defined.}

Here is the distribution for the homogeneous case. Although it is not
noticeable in the histogram, there are various photons that escape
with a low number of scatterings (i.e. the minimum number of
scatterings we found for some photons is 2).

We have modified the caption to define the solid and dashed lines.

\begin{center}
\includegraphics[width=0.6\textwidth]{./f9h.png}
\end{center}

### 2014-08-11 paper/referee-reply.tex

\title{Response to the second report on the article draft \emph{The
    Impact of Gas Bulk Rotation on the Lyman-$\alpha$ line.}} 
\author{Juan N. Garavito-Camargo, Jaime E. Forero-Romero, Mark Disjkstra}
\date{\today}

\begin{document}

\maketitle

We thanks the referee for the new comments, suggestions and remars.
In what follows the comments by the referee are boldfaced.

### 2014-08-12 paper/ms.tex
arxiv version

We present results of radiative transfer calculations to measure the
impact of gas bulk rotation on the morphology of the Lyman $\alpha$ 
emission line in distant galaxies. 
We model a galaxy as a sphere with an homogeneous mixture of dust and
hydrogen at a constant temperature. 
These spheres have a solid-body rotation with maximum velocities in
the range $0-300$ \kms and neutral hydrogen optical depths in the
range $\tau_{\rm H}=10^{5}-10^{7}$. 
We consider two types of source distributions in the sphere: central and 
homogeneous.
Our main result is that rotation introduces a dependence of the
line morphology with  viewing angle and rotational velocity. 
Observations with a line of sight parallel to the rotation axis yield
line morphologies similar to the static case. 
For lines of sight perpendicular to the rotation axis both the intensity at the line
center and the line width increase with rotational velocity.   
Along the same line of sight, the line becomes single peaked  at rotational
velocities close to half the line width in the static case. 
Notably, we find that rotation does not induce any significant spatial
anisotropy in the integrated line flux, the escape fraction or the
average number of scatterings. From this, we conclude that the \lya scattering
through a rotating solid-body proceeds identical to the static
case. The only difference is the doppler shift from the different
regions in the sphere that move with respect to the observer. This
allows us to derive an analytic approximation for the viewing-angle
and rotational velocity of the emerging spectrum.
\end{abstract}

>>>>

We present results of radiative transfer calculations to measure the
impact of gas bulk rotation on the morphology of the Lyman $\alpha$ 
emission line in distant galaxies. 
We model a galaxy as a sphere with an homogeneous mixture of dust and
hydrogen at a constant temperature. 
These spheres undergo solid-body rotation with maximum velocities in
the range $0-300$ \kms and neutral hydrogen optical depths in the
range $\tau_{\rm H}=10^{5}-10^{7}$. 
We consider two types of source distributions in the sphere: central and 
homogeneous.
Our main result is that rotation introduces a dependence of the
line morphology with  viewing angle and rotational velocity. 
Observations with a line of sight parallel to the rotation axis yield
line morphologies similar to the static case. 
For lines of sight perpendicular to the rotation axis both the intensity at the line
center and the line width increase with rotational velocity.   
Along the same line of sight, the line becomes single peaked  at rotational
velocities close to half the line width in the static case. 
Notably, we find that rotation does not induce any spatial anisotropy in the integrated line flux, the escape fraction or the average number of scatterings. This is because Lyman α scattering through a rotating solid-body proceeds identical as in the static case. The only difference is the doppler shift from the different
regions in the sphere that move with respect to the observer. This
allows us to derive an analytic approximation for the viewing-angle
and rotational velocity of the emerging spectrum.
\end{abstract}
